\section{Expected Challenges and Mitigation Strategies}

I anticipate four principal challenges.

\vspace{-8pt}\paragraph{Challenge 1: Denmark-to-GRACE Scale Mismatch.}
The native resolution of \textbf{GRACE} is around 300\nobreakspace km versus a national area of about 43,000\nobreakspace km\textsuperscript{2}. This will be mitigated through sub-monthly data assimilation, ConBay merging with higher-resolution \textbf{SMAP}, machine learning-based downscaling validated against Jupiter, and rigorous \textbf{GIA} correction.
\smallskip

\vspace{-8pt}\paragraph{Challenge 2: Equifinality and Identifiability.}
Joint state and parameter estimation under large observation uncertainty risks multiple parameter sets fitting equally well. This will be mitigated through \textbf{GEUS}-derived priors on aquifer parameters, localisation and inflation in \textbf{LETKF}, and dPL as a deterministic precursor before stochastic data assimilation.
\smallskip

\vspace{-8pt}\paragraph{Challenge 3: Integrating Machine Learning Without Losing Physical Consistency.}
Adding neural components can erode interpretability and physical fidelity. This will be handled by keeping VIC DK as the physical backbone, restricting the \textbf{LSTM} to a residual post-processor role, and applying conformal prediction for honest uncertainty bounds.
\smallskip

\paragraph{Challenge 4: Combined Index Collapse into Smoothed Average.}
A multi-pillar index risks collapsing into a smoothed average, losing signal contrast. This will be mitigated by pillar-appropriate time scales (\textbf{SPI} on 1--3\nobreakspace months, \textbf{SGI} on 6--12\nobreakspace months), copula aggregation that preserves tail dependence, and hierarchical validation against Naturskaderådet impact claims, crop yield anomalies, and \textbf{EDO CDI v4}.
